### 2022-12-22 docs/src/_intro.qmd
helper function for bootstrap with caching and multi-threading
moved stuff out of here

## Research Paper 📝

**Note** ⚠: You are browsing the [`#original-paper`](https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl/tree/original-paper) branch of `AlgorithmicRecourseDynamics.jl`. This branch is a static artifact corresponding to the state of the package at the time the paper was first published. It can be used to replicate the original findings of the paper.

## At a Glance

You can find resources relevant to the paper right here on this branch of the
repository:

- [Paper](paper/paper.pdf)
- [Notebooks](dev/notebooks/)
- [Supplementary Appendix](build/dev/notebooks/appendix.html) generated from notebooks (download the HTML and view in browser)
- [Artifacts]() (including data and experimental results; link currently exluded due to double-blind review process)

@@

## Paper Abstract

Existing work on Counterfactual Explanations (CE) and Algorithmic Recourse (AR) has largely focused on single individuals in a static environment: given some estimated model, the goal is to find valid counterfactuals for an individual instance that fulfill various desiderata. The ability of such counterfactuals to handle dynamics like data and model drift remains a largely unexplored research challenge. There has also been surprisingly little work on the related question of how the actual implementation of recourse by one individual may affect other individuals. Through this work we aim to close that gap. We first show that many of the existing methodologies can be collectively described by a generalized framework. We then argue that the existing framework does not account for a hidden external cost of recourse, that only reveals itself when studying the endogenous dynamics of recourse at the group level. Through simulation experiments involving various state-of-the-art counterfactual generators and several benchmark datasets, we generate large numbers of counterfactuals and study the resulting domain and model shifts. We find that the induced shifts are substantial enough to likely impede the applicability of Algorithmic Recourse in some situations. Fortunately, we find various strategies to mitigate these concerns. Our simulation framework for studying recourse dynamics is fast and open-sourced.

>>>>

## Related Research Paper 📝

@@
